Spatiotemporal Visualization

### 2022-05-26 doc/spatiotemp-viz.Rmd
adjust CLUTO to new approach and update test snapshots

```{r, fig.align='center', eval=os&&!is_cran&&pkgdown, fig.width=8, fig.height=9}
library(mlr3)
library(mlr3spatiotempcv)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv_cluto", folds = 5, time_var = "Date")
resampling$instantiate(task_st)

>>>>

```{r, fig.align='center', eval=os&&!is_cran&&pkgdown, fig.width=8, fig.height=9}
library(mlr3)
library(mlr3spatiotempcv)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv_cluto", folds = 5)
resampling$instantiate(task_st)
